Panel Seminars

### 2021-05-19 index.Rmd
Add link to RAD panel video

| Date        | Topic       | Panelists     |
| :---        | :---        | :---          |
| May 7         | GBS/RADseq genotyping pipelines     | [Melanie LaCava](https://melanielacava.weebly.com/), [Alicia Mastretta-Yanes](http://mastrettayanes-lab.org/), [Isaac Overcast](https://isaacovercast.github.io/), [Jon Puritz](https://www.marineevoeco.com/)   |
| May 21       |  WGS genotyping (low and high coverage)     | [Jeffrey Good](http://www.thegoodlab.org/), [Mikhail "Misha" Matz](https://matzlab.weebly.com/), [Noah Reid](http://nreid.github.io/), [Tim Sackton](https://scholar.harvard.edu/tsackton), [Nina Overgaard Therkildsen](https://www.therkildsenlab.com/) |
| June 4       |  Population genomic analyses and filtering data     | [Zach Gompert](https://gompertlab.com/), [Morgan Kelly](http://www.morgankelly.biology.lsu.edu/), [Katie Lotterhos](https://sites.google.com/site/katielotterhos/home), [Jeff Ross-Ibarra](https://rilab.ucdavis.edu/) |
| June 18       |  Functional Genomics (RNAseq)     | [Ana Conesa](http://conesalab.org/), [Joanna Kelley](https://labs.wsu.edu/genomes/), TBD|

>>>>

| Date        | Topic       | Panelists     | Video     |
| :---        | :---        | :---          | :---      |
| May 7         | GBS/RADseq genotyping pipelines     | [Melanie LaCava](https://melanielacava.weebly.com/), [Alicia Mastretta-Yanes](http://mastrettayanes-lab.org/), [Isaac Overcast](https://isaacovercast.github.io/), [Jon Puritz](https://www.marineevoeco.com/)   | [View video](https://www.youtube.com/watch?v=C74GBESeIq4)     |
| May 21       |  WGS genotyping (low and high coverage)     | [Jeffrey Good](http://www.thegoodlab.org/), [Mikhail "Misha" Matz](https://matzlab.weebly.com/), [Noah Reid](http://nreid.github.io/), [Tim Sackton](https://scholar.harvard.edu/tsackton), [Nina Overgaard Therkildsen](https://www.therkildsenlab.com/) |     |
| June 4       |  Population genomic analyses and filtering data     | [Zach Gompert](https://gompertlab.com/), [Morgan Kelly](http://www.morgankelly.biology.lsu.edu/), [Katie Lotterhos](https://sites.google.com/site/katielotterhos/home), [Jeff Ross-Ibarra](https://rilab.ucdavis.edu/) |     |
| June 18       |  RNAseq (experimental design through differential expression)     | [Ana Conesa](http://conesalab.org/), [Joanna Kelley](https://labs.wsu.edu/genomes/), [Martin Hölzer](https://hoelzer-lab.github.io/), TBD     |     |
